Quality Definitions of Qualities

### 2019-10-09 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
Updates lipics-v2019 so can compile, also switched back to natbib to get bib to work
Added initial definitions for reproducibility, unambiguity, verifiability and abstract.  Closes #5

\subsection{Visibility/Transparency}
    \ad{I found little contents related to visibility or transparency. The following definition is the only one I could find, but may be irrelevant to this project.}
    \begin{quotation}
        1. the degree to which a transaction can access object state concurrently with other transactions. 2. the specification, for a property, of "who can see it?"~\cite{ISO/IEC/IEEE24765}
    \end{quotation}
\subsection{Reproducibility}

@@

@@

\begin{quotation}
    The best definition of the productivity of a process is
    \[Productivity = \dfrac{Outputs\ produced\ by\ the\ process}{Inputs\ consumed\ by\ the\ process}\]
    Defining inputs. For the software process, providing a meaningful definition of inputs is a nontrivial but generally workable problem. Inputs to the software process generally comprise labor, computers, supplies, and other support facilities and equipment. Defining outputs. The big problem in defining software productivity is defining outputs. Here we find a paradox. Most sources say that defining delivered source instructions (DSI) or lines of code as the output of the software process is totally inadequate, and they argue that there are a number of deficiencies in using DSI. However, most organizations doing practical productivity measurement still use DSI as their primary metric~\cite{Boehm1987}.\\

    \smallskip
    Productivity is the amount of output (what is produced) per unit of input used.If we can measure the size of the software product and the effort required to develop the product, we have:
    \begin{align}
        productivity = size/effort
    \end{align}
    Equation (1) assumes that size is the output of the software production process and effort is the input to the process. This can be contrasted with the viewpoint of software cost models where we use size as an independent variable (i.e., an input) to predict effort which is treated as an output. Equation (1) is simple to operationalize if we have a single dominant size measure, for example, product size measured in lines of code~\cite{Kitchenham2004}.
\end{quotation}

@@

Documentation is said to be unambiguous only when every requirement's
specification has a unique interpretation.  The documentation should be
unambiguous to all audiences, including developers, users and reviewers.

@@

Every requirement in the documentation must be the one fulfilled by the
implemented software. Therefore all the requirements should be clear,
unambiguous and testable, so that a person or a machine can verify whether the
software product meets the requirements.

@@

Documented requirements are said to be abstract if they state what the software
must do and the properties it must possess, but do not speak about how these are
to be achieved. For example, a requirement can specify that an Ordinary
Differential Equation (ODE) must be solved, but it should not mention that
Euler's method should be used to solve the ODE. How to accomplish the
requirement is a design decision, which is documented during the design phase.

@@

\bibliographystyle {plainurl}
\bibliography {../../CommonFiles/ResearchProposal}

>>>>

\subsection{Visibility/Transparency}
    \ad{I found little contents related to visibility or transparency. The following definition is the only one I could find, but may be irrelevant to this project.}
    \begin{quotation}
        1. the degree to which a transaction can access object state concurrently with other transactions. 2. the specification, for a property, of "who can see it?"~\cite{ISO/IEC/IEEE24765}
    \end{quotation}

\subsection{Reproducibility}

@@

Reproducibility is defined as:

A result is said to be reproducible if another researcher can take the original
code and input data, execute it, and re-obtain the same result (Peng, Dominici,
and Zeger, 2006), as cited in \citet{BenureauAndRougier2017}.

The related concept of replicable is defined as:

Documentation achieves replicability if the description it provides of the
algorithms is sufficiently precise and complete for an independent researcher to
re-obtain the results it presents.  \citep{BenureauAndRougier2017}

It would be worthwhile to look for some additional definitions.

@@

\begin{quotation}
    The best definition of the productivity of a process is
    \[\text{Productivity} = \dfrac{\text{Outputs produced by the
          process}}{\text{Inputs consumed by the process}}\]
    Defining inputs. For the software process, providing a meaningful definition
    of inputs is a nontrivial but generally workable problem. Inputs to the
    software process generally comprise labor, computers, supplies, and other
    support facilities and equipment. Defining outputs. The big problem in
    defining software productivity is defining outputs. Here we find a
    paradox. Most sources say that defining delivered source instructions (DSI)
    or lines of code as the output of the software process is totally
    inadequate, and they argue that there are a number of deficiencies in using
    DSI. However, most organizations doing practical productivity measurement
    still use DSI as their primary metric~\cite{Boehm1987}.

    \smallskip
    Productivity is the amount of output (what is produced) per unit of input used.If we can measure the size of the software product and the effort required to develop the product, we have:
    \begin{align}
        \text{productivity} = \text{size}/\text{effort}
    \end{align}
    Equation (1) assumes that size is the output of the software production
    process and effort is the input to the process. This can be contrasted with
    the viewpoint of software cost models where we use size as an independent
    variable (i.e., an input) to predict effort which is treated as an
    output. Equation (1) is simple to operationalize if we have a single
    dominant size measure, for example, product size measured in lines of
    code~\cite{Kitchenham2004}.
\end{quotation}

@@

A specification is unambiguous when it has a unique interpretation.  If there is
a possibility that two readers will have two different interpretations, than the
specification is ambiguous.  \wss{When I get the Ghezzi text back from Olu, I'll
  check to see if they have anything to add to this definition.}

A Software Requirements Specification (SRS) is unambiguous if, and only if,
every requirement stated therein has only one interpretation \citep{IEEE1998}.

@@

\begin{itemize}

\item Verification - Are we building the product right?  Are we implementing the
  requirements correctly (internal)
\item Validation - Are we building the right product? Are we getting the right
  requirements (external)
\item According to
  \href{https://en.wikipedia.org/wiki/Software_verification_and_validation}{Capability
    Maturity Model (CMM)}
\begin{itemize}
\item 
    Software Verification: The process of evaluating software to determine
    whether the products of a given development phase satisfy the conditions
    imposed at the start of that phase. [IEEE-STD-610]
  \item Software Validation: The process of evaluating software during or at the
    end of the development process to determine whether it satisfies specified
    requirements. [IEEE-STD-610] 
\end{itemize}
\end{itemize}

``An SRS is verifiable if, and only if, every requirement stated therein is
verifiable. A requirement is verifiable if, and only if, there exists some
finite cost-effective process with which a person or machine can check that the
software product meets the requirement. In general any ambiguous requirement is
not verifiable.'' \citep{IEEE1998}

Verifiability is related to testability, which is defined by McCall et al.\ as
``The effort required to test a program to ensure that it performs its intended
function'' \cite{VanVliet2000}.

\wss{When I get the Ghezzi text back from Olu,
  I'll check to see if they have anything to add to this definition.}

@@

Documented requirements are said to be abstract if they state what the software
must do and the properties it must possess, but do not speak about how these are
to be achieved \citep{GhezziEtAl2003}.

``An abstraction for a software artifact is a succinct description that suppresses
the details that are unimportant to a software developer and emphasizes the
information that is important.'' \cite{Krueger1992}

``Abstraction means that we concentrate on the essential features and ignore,
abstract from, details that are not relevant at the level we are currently
working.''  \cite[p.\ 296]{VanVliet2000}

``Abstraction in mathematics is the process of extracting the underlying essence
of a mathematical concept, removing any dependence on real world objects with
which it might originally have been connected, and generalizing it so that it
has wider applications or matching among other abstract descriptions of
equivalent phenomena.''
\href{https://en.wikipedia.org/wiki/Abstraction_(mathematics)} {Wikipedia
  Definition}

Abstraction is related to reusability (and other qualities).

\wss{When I get the Ghezzi text back from Olu, I'll check to see if they have
  anything to add to this definition.}

@@

\bibliographystyle {plainnat}
\bibliography {../../CommonFiles/ResearchProposal}
